%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Freelance Pirate} % Job title
{Captain of the Black Pearl} % Organization
{Caribbean Sea} % Location
{1700 - \textsc{Present}} % Date(s)
{
\begin{cvitems}
\setlength{\itemsep}{1ex} %
% 
\item Main achievements:
\begin{cvitemsnested}
    \item{Commanded the fastest ship in the Caribbean, known for its ability to outrun both naval ships and rival pirates.}
    \item{Successfully navigated through treacherous waters, including the Devil's Triangle and the Isla de Muerta.}
    \item{Led numerous successful raids and treasure hunts, acquiring vast wealth (and occasionally losing it all).}
    \item{Notable escapades include retrieving the cursed Aztec gold, escaping the clutches of the Kraken, and defeating the undead pirate Hector Barbossa.}
    \item{Expert in negotiation and persuasion, often using unconventional methods to outwit enemies and allies alike.}
\end{cvitemsnested}
\item Additional responsibilities
    \begin{cvitemsnested}
    \item {Keep ship stocked with food, treasure and rum.}
    \item {Conquer any mutiny.}
    \end{cvitemsnested}
\end{cvitems}
}

\cventry
{Pirate Lord of the Caribbean Sea} % Job title
{Brethren Court} % Organization
{Caribbean } % Location
{1692 - \textsc{Present}} % Date(s)
{
\begin{cvitems}
\setlength{\itemsep}{1ex} %
%
% ---
\item {Played a pivotal role in the fight against the East India Trading Company and the pirate hunter Lord Cutler Beckett. \hfill \cgitproject{sample-project}}
\item {Instrumental in the liberation of the sea goddess Calypso, restoring balance to the seas. \hfill \cpaperlink{https://en.wikipedia.org/wiki/Calypso_(mythology)}}
\item {Instructor for new sailors.}
\end{cvitems}
}

\cventry
{Former Captain of the HMS Interceptor}
{Royal Navy (Briefly)}
{Caribbean Sea} % Location
{1690} % Date(s)
{
\begin{cvitems}
\setlength{\itemsep}{1ex} %
% ---
\item {Briefly commandeered a Royal Navy vessel, utilizing it for pirate activities before its untimely destruction.}
\item {Demonstrated a unique ability to infiltrate and commandeer naval vessels with minimal resources.}
%
\end{cvitems}
}

\cventry
{Internship Opportunity: Pirate Apprentice} % Job title
{Black Pearl Enterprises} % Organization
{Caribbean Sea (Mobile)} % Location
{1688} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Assist in navigating the Caribbean Sea using both traditional and magical instruments.}
\item {Participate in raids, skirmishes, and treasure hunts, ensuring compliance with pirate codes.}
\item {Maintain and repair ship equipment, including sails, rigging, and cannons.}
\item {Learn to interpret maps, decrypt hidden messages, and use the Compass of Uncertainty.}
\item {Contribute to the acquisition and management of rum supplies.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

