%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}[Sailing projects]
%------------------------------------------------
% \vspace*{-2mm}
\cventry
{Operation Golden Horizon} % Project title
{}{}
{Exp. 2025-2026} % Duration
{ % Description(s) of tasks/responsibilities
\vspace{-4mm}
\begin{cvitemsnested}
    \item {Chart a course to uncover a hidden island rumored to contain vast amounts of Aztec gold.}
\end{cvitemsnested}
\vspace{-4mm}
}

\cventry
{Quest for Neptune’s Trident} % Project title
{}{}
{Exp. 2025-2029} % Duration
{ % Description(s) of tasks/responsibilities
\vspace{-4mm}
\begin{cvitemsnested}
    \item {Retrieve the mythical Trident of Poseidon to control the seas and end all curses upon the ocean.}
\end{cvitemsnested}
\vspace{-4mm}
}

\cventry
{Fortune in the Deep} % Project title
{}{}
{2025-2029} % Duration
{ % Description(s) of tasks/responsibilities
\vspace{-4mm}
\begin{cvitemsnested}
    \item {Salvage a sunken Spanish galleon loaded with precious cargo lost in a violent storm.}
    \item {Get intercepted by merchants upon return, successfully battled and saved the cargo. }
\end{cvitemsnested}
\vspace{-4mm}
}

\cventry
{Echoes of the Black Armada} % Project title
{}{}
{2025-2029} % Duration
{ % Description(s) of tasks/responsibilities
Investigate reports of ghostly ships attacking merchant vessels and discover the source of their wrath.
}

\cventry
{Pirate Council Conclave} % Project title
{}{}
{2023-2028} % Duration
{ % Description(s) of tasks/responsibilities
Convene the Brethren Court to discuss a unified defense against the growing threat of the East India Trading Company.
}

\cventry
{Cursed Coins Retrieval} % Project title
{}{}
{2023-2027} % Duration
{ % Description(s) of tasks/responsibilities
Collect all 882 cursed Aztec coins scattered across the Caribbean to lift a deadly curse.
}

\cventry
{Rum Runner’s Revenge (RRR)} % Project title
{}{}
{2024-2028} % Duration
{ % Description(s) of tasks/responsibilities
Reclaim a stolen shipment of rum from a rival pirate crew, restoring Jack's honor and supplies.
}

\cventry
{Mystery of the Phantom Isle} % Project title
{}{}
{2024-2028} % Duration
{ % Description(s) of tasks/responsibilities
Explore an uncharted island that appears and disappears with the tide, hiding ancient secrets.
}
\end{cventries}

\begin{cventries}[Mainland projects]
\cventry
{Whispering Sands Rescue} % Project title
{}{}
{2022-2023} % Duration
{ % Description(s) of tasks/responsibilities
Rescue a stranded pirate crew trapped on a desert island beset by quicksand and hostile creatures.
}

\cventry
{Storm the Bastille Bay} % Project title
{}{}
{2019-2024} % Duration
{ % Description(s) of tasks/responsibilities
Launch an assault on a heavily fortified port to free imprisoned allies and gain strategic advantage
}

\cventry
{Black Market Heist} % Project title
{}{}
{2018-2022} % Duration
{ % Description(s) of tasks/responsibilities
Infiltrate a clandestine pirate auction to retrieve a stolen piece of Jack’s heritage.
}

\cventry
{Sirens of the Silver Reef} % Project title
{}{}
{2016-2017} % Duration
{ % Description(s) of tasks/responsibilities
Negotiate a truce with the Sirens who haunt the Silver Reef, notorious for luring ships to their doom.
}

\cventry
{Inferno of the Ivory Coast} % Project title
{}{}
{2015-2019} % Duration
{ % Description(s) of tasks/responsibilities
\vspace{-4mm}
\begin{cvitemsnested}
    \item {Rescue a kidnapped crewmember held by ruthless slavers along the Ivory Coast.}
    \item {Track and confront the legendary Kraken, which has been terrorizing shipping lanes and coastal towns.} 
    \item {Stakeholder management slavetraders, Kraken and academic partners.}
\end{cvitemsnested} 
\vspace{-4mm}
}

\end{cventries}
